Contextual Combinatorial Cascading Bandits

### 2015-12-05 contextual combinatorial cascading bandits.tex

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. 
First, the learning agent 
	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm}
\caption{ConComCascade}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
%\STATE{}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward in all time under the conjunctive objective and let $p_{t, \bA_t}$ (resp., $p_{\wedge, t, \bA_t}$) are probabilities that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under disjunctive objective(resp., conjunctive), that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under disjunctive case. Here is our main theorem.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$$
\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}.
$$
Let regularization parameter satisfy $\lambda \geq C_\gamma$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
\begin{equation}
\begin{split}
&R(T) = \frac{\sqrt{2}}{p^*} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda}) \\
&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)},
\end{split}
\end{equation}
\begin{equation}
\begin{split}
&R_{\wedge}(T) = \frac{\sqrt{128}}{f_{\wedge}^{\ast}} (\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log(\frac{1}{\delta})} + \sqrt{\lambda})\\
&\qquad \qquad \cdot \sqrt{TKd\log(\lambda + C_\gamma T/d)}.
\end{split}
\end{equation}
where
\begin{align*}
C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
\end{align*}
\end{theorem}

>>>>

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. 
First, the learning agent 
	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm}
\caption{C$^3$-UCB}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
%\STATE{}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed under the 
disjunctive objective. The following is the main theorem on the regret achieved by
	our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$,
	where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{equation}
\begin{split}
&R(T) \le \frac{\sqrt{2}}{p^*} \sqrt{TKd\log(\lambda + C_\gamma T/d)}  \\
&\qquad \qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right),
\end{split}
\end{equation}
\begin{equation}
\begin{split}
&R_{\wedge}(T) \le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\log(\lambda + C_\gamma T/d)} \\
&\qquad \qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right).
\end{split}
\end{equation}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}
